Ranking Stability

### 2021-08-11 output_scripts/investigate_rankings.Rmd
look at parameter recovery for simulation studies also

@@

@@

  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
  m1_ranks <- apply(f_m1, 2, mean)

@@

  f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
  m2_ranks <- apply(f_m2, 2, mean)

@@

  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
  m3_ranks <- apply(f_m3, 2, mean)

@@

```{r eta_recovery}

eta_ests <- tibble()

@@

  eta_m1 <- sim_model3_stan_sim1 %>% 
    select(starts_with("eta")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = mean(value)) %>% 
    mutate(model = "C-HP")

  eta_m2 <- sim_model3_stan_sim2 %>%
    select(starts_with("eta")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = mean(value)) %>% 
    mutate(model = "C-DCHP")

  eta_m3 <- sim_model3_stan_sim3 %>%
    select(starts_with("eta")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = mean(value)) %>% 
    mutate(model = "C-MMHP")

  curr_sim_ests <- bind_rows(eta_m1,
                             eta_m2,
                             eta_m3)

  eta_ests <- eta_ests %>% 
    bind_rows(curr_sim_ests)

@@

tru_values <- tibble(name = c("eta_1", "eta_2", "eta_3"),
                     mean_est = c(object_par$sim_eta_1,
                                  object_par$sim_eta_2,
                                  object_par$sim_eta_3))

eta_ests %>% 
  ggplot(aes(name, mean_est)) +
  geom_boxplot(aes(fill = model)) +
  geom_hline(mapping = aes(yintercept = mean_est),
             tru_values, colour = "red") +
  facet_wrap(~name)

@@

>>>>

mean_values <- cohort_est %>% select(variable, mean)

@@

f_vec <- seq(from = 0.2, to = 0.9, length.out = num_nodes)

@@

  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
  m1_ranks <- apply(f_m1, 2, median)

@@

  f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
  m2_ranks <- apply(f_m2, 2, median)

@@

  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
  m3_ranks <- apply(f_m3, 2, median)

@@

```{r eta_recovery}
eta_ests <- tibble()

@@

  eta_m1 <- sim_model3_stan_sim1 %>% 
    select(starts_with("eta") | starts_with("beta") |
             starts_with("r_lam")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = median(value)) %>% 
    mutate(model = "C-HP") %>% 
    filter(name != "beta_delta")

  eta_m2 <- sim_model3_stan_sim2 %>%
    select(starts_with("eta") | starts_with("beta") |
             starts_with("r_lam")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = median(value)) %>% 
    mutate(model = "C-DCHP") %>% 
    filter(name != "beta_delta")

  eta_m3 <- sim_model3_stan_sim3 %>%
    select(starts_with("eta") | starts_with("beta") |
             starts_with("r_lam")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = median(value)) %>% 
    mutate(model = "C-MMHP") %>% 
    filter(name != "beta_delta")

  curr_sim_ests <- bind_rows(eta_m1,
                             eta_m2,
                             eta_m3)
  eta_ests <- eta_ests %>% 
    bind_rows(curr_sim_ests)
}

@@

tru_values <- tibble(name = c("eta_1", "eta_2", "eta_3",
                              "r_lambda1", "beta"),
                     mean_est = c(object_par$sim_eta_1,
                                  object_par$sim_eta_2,
                                  object_par$sim_eta_3,
                                  object_par$sim_w_lam,
                                  object_par$sim_beta))

eta_ests %>% 
  ggplot(aes(name, mean_est)) +
  geom_boxplot(aes(fill = model)) +
  geom_hline(mapping = aes(yintercept = mean_est),
             tru_values, colour = "red") +
  facet_wrap(~name, scales = "free")

@@

Similarly, we can check the degree parameters.

```{r gamma-estimates}
gamma_ests <- tibble()

  gamm_m2 <- sim_model3_stan_sim2 %>%
    select(starts_with("gamma") ) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = median(value)) %>% 
    mutate(model = "C-DCHP")

  gamm_m3 <- sim_model3_stan_sim3 %>%
    select(starts_with("gamma") ) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = median(value)) %>% 
    mutate(model = "C-MMHP")

  curr_sim_ests <- bind_rows(gamm_m2,
                             gamm_m3)
  gamma_ests <- gamma_ests %>% 
    bind_rows(curr_sim_ests)
}

gamma_ests$model <- factor(gamma_ests$model, levels = c("C-HP",
                                                    "C-DCHP",
                                                    "C-MMHP"))

tru_values <- tibble(name = paste0("gamma[", 1:num_nodes, "]"),
                     mean_est = object_par$gamma_var)

gamma_ests %>% 
  ggplot(aes(name, mean_est)) +
  geom_boxplot(aes(fill = model)) +
  geom_hline(mapping = aes(yintercept = mean_est),
             tru_values, colour = "red") +
  facet_wrap(~name, scales = "free")
```

```{r gamma-estimates}
zeta_ests <- tibble()

  zeta_m2 <- sim_model3_stan_sim2 %>%
    select(starts_with("zeta") ) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = median(value)) %>% 
    mutate(model = "C-DCHP")

  zeta_m3 <- sim_model3_stan_sim3 %>%
    select(starts_with("zeta") ) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = median(value)) %>% 
    mutate(model = "C-MMHP")

  curr_sim_ests <- bind_rows(zeta_m2,
                             zeta_m3)
  zeta_ests <- zeta_ests %>% 
    bind_rows(curr_sim_ests)
}

zeta_ests$model <- factor(zeta_ests$model, levels = c("C-HP",
                                                    "C-DCHP",
                                                    "C-MMHP"))

tru_values <- tibble(name = paste0("zeta[", 1:num_nodes, "]"),
                     mean_est = object_par$zeta_var)

zeta_ests %>% 
  ggplot(aes(name, mean_est)) +
  geom_boxplot(aes(fill = model)) +
  geom_hline(mapping = aes(yintercept = mean_est),
             tru_values, colour = "red") +
  facet_wrap(~name, scales = "free")
```
